\documentclass{article}
\usepackage{graphicx} % Required for inserting images
\usepackage{hyperref}
\title{san francisco plane latency}
\author{}
\date{}
\begin{document}

\maketitle

\section{rules}
\begin{itemize}
    \item 50 coins per 0.1 miles on bus
    \item 60 coins per 0.1 miles on foot
    \item \textbf{All teams start at San Francisco Day School, Golden Gate Ave Entrance.}
    \item \textbf{Game starts at 10:30am and ends at 3:30pm.}
    \item \textbf{You start the game by randomly picking three challenges. When you complete a challenge, randomize for a new challenge, using \url{https://plane-latency.vercel.app/challenges}.}
    \item \textbf{For every challenge you must take a photo/video as proof that you completed the challenge. Afterwards, send the photo and challenge name to your opponents in the relevant Discord channel.}
    \item \textbf{If you would like another challenge option, you can veto a challenge, whereby you must stay in the same place for 15 minutes and you cannot complete any challenges.}
    \item \textbf{If you've completed or vetoed a challenge, you can't do it again.}
    \item \textbf{At any point you are allowed to walk away from your current station/bus stop as long as you walk back to it for no cost. This will be very useful for most challenges.}
    \item \textbf{There are 3 teams. There are two types of team: Harvesters and Crops. At all points in the game, there are 2 teams of type Harverster, (2 Harvesters) and 1 team of type Crop (1 Crop).}
    \item \textbf{Only the Crop needs to pay coins to move, and only the Crop can complete challenges and do curses.}
    \item \textbf{The Harvesters have access to the Crop's location, but the Crop does not have access to the Harvesters' location.}
    \item \textbf{The Harvesters work in collaboration to try to "harvest" the Crop by physically tapping on any part of a Crop team member. If a Harvester harvests the Crop, then the next team in the Crop Rotation becomes the new Crop (and the old Crop becomes a Harvester). }
    \item \textbf{The two Harvester teams must stay within 1 minute walk of each other. }
    \item \textbf{Each team also has an target location; whenever a team is a Crop, they attempt to move towards their location. If at any point a Crop reaches their target location, they win.}
    \item \textbf{Each team has a crop as its name. The names of teams are: Fish, Apple, and Applesauce. Fish's target location is Fisherman's Wharf Musée Mécanique entrance. Apple's target location is Legion of Honor Museum Gift Store. Applesauce's target location is Glen Canyon Creeks to Peaks North Trailhead. }
    \item \textbf{At the beginning of the game, a draft order is randomly selected. There will be two rounds in the draft. For their pick, a team may either select an target location or a place in the Crop Rotation. If in the first round of the draft, a team picks an target location, in the second round, they must pick a place in the Crop Rotation, and vice versa.}
    \item \textbf{At the end of the game, if no Crop has reached the target location, the team whose target location is closest to the current Crop wins.}
\end{itemize}

\section{challenges}
\begin{enumerate}
    \setcounter{enumi}{-1}
    \item \textbf{SPICIEST FOOD} \\ Go to a restaurant and ask for the spiciest thing on the menu. You must take a photo of the item and send it to your opponents. You must finish the entire food before proceeding. It must be described by the restaurant as spicy/hot  \textbf{300 coins}
    \item \textbf{BREAK ANY LAW} \\ Break a law. The law can be from any level of jurisdiction and does not have to be a law in California. \textbf{100 coins}
    \item \textbf{TAKE A PICTURE OF AN OFFICIAL SAN FRANCISCO LANDMARK} \\ You must be within 100 feet of the landmark when the photo is taken. Find landmarks at \url{https://en.wikipedia.org/wiki/List_of_San_Francisco_Designated_Landmarks} \textbf{200 coins}
    \item \textbf{FIND ANY COIN ON THE GROUND} \\ The coin does not have to be American. It must be a metal coin and valid currency in somewhere (not necessarily a country currency) \textbf{150 coins}
    \item \textbf{HOUSESHOPPING}\\ Estimate the value of a house at your current location. You must then check on Zillow for the value of the house. Your guess must be within 25\%. If incorrect, you must veto. \textbf{500 coins}
    \item \textbf{DO 50 JUMPING JACKS} \\ Do 50 jumping jacks. You must record the whole thing. Only one person may perform the jumping jacks at a time but gyou can cumulative add the team member's jumping jacks to get to 50. \textbf{100 coins}
    \item \textbf{FIND A FANCY CAR} \\ Take a picture of car that has a price of \$100,000 or more \textbf{300 coins}
    \item \textbf{TOUCH STRANGER'S DOG} \\ Touch a stranger's dog. You must get permission. \textbf{150 coins}
    \item \textbf{CRITICS} \\ Record a 5-minute video criticizing the nearest building to you. You must continuously criticize the building for 5 minutes straight. You may switch who is speaking, but it must be one uncut video of at least 5 minutes long. \textbf{200 coins}
    \item \textbf{ADVERTISE ARC} \\ You must make a sign with the arc logo and adhere it to some spot at least 3 feet above the ground. It must stick without any human body part touching it. The arc logo can be makeshift but it must still be recognizably arc. \textbf{300 coins}
    \item \textbf{COO-L PIGEON} \\ Get close enough to a pigeon to take a picture with both the pigeon and your feet in it. You must have both feet of one person in said photo. \textbf{300 coins}
    \item \textbf{PROUD ARC USER} \\ Randomly pick 30 seconds of audio from a video on the browser company's youtube channel. Memorize it and repeat it on camera. First, sort the videos of newest to oldest and randomize a number to pick which video. Then randomize a number to pick when to start your video. If at any point you do not have at least 30 seconds, rerandomize. \textbf{500 coins}
    \item \textbf{NEAREST MUNI \& BART} \\ Take picture of the nearest BART \& MUNI station. There must be a BART sign with the station name in one picture and a MUNI sign with the station name in another. You must also send the address of the point you started from so one can verify the nearest MUNI \& BART station. \textbf{300 coins}
    \item \textbf{RUN A HALF-MILE} \\ You must return to where you started at the end of the half-mile. \textbf{200 coins}
    %\item \textbf{TOUCH THE OCEAN} \\ Touch the ocean. You can do it on either the west, north, or east of San Francisco. If you cannot touch the ocean, you can also collect the coins if you are directly above the water, etc on a pier) \textbf{500 coins}
    \item \textbf{FIND A FOREIGN FLAG} \\ Find a foreign flag. You must be able to identify what country flag it is. \textbf{100 coins}
    \item \textbf{GREEN IN GREEN} \\ Go to a place colored green on google maps and take a picture with something green in that park. \textbf{100 coins}
    \item \textbf{GIVE ME A SIGN} \\ Photograph a street sign with a street name that contains a number (word or digits) \textbf{100 coins}
    \item \textbf{CLIMB A TREE} \\ Climb a tree. You must record yourself touching only the tree and not the ground or roots of the tree for 5 seconds. \textbf{100 coins}
    \item \textbf{VISIT A MUSEUM} \\ Go into a museum and stay there for at least 5 minutes. Share a fact that you learned on camera. \textbf{300 coins}
    \item \textbf{USE A FANCY RESTROOM} \\ Go into a bathroom of a hotel that offers a room over \$500 \textbf{500 coins}
    \item \textbf{GO EXACTLY HALF A MILE} \\ First, set a starting point. Then from there, spin around and point in a random direction. You must then go to a point at least a half-mile in that direction. Unlike other challenges, you don't have to return to where you started. \textbf{200 coins}
    \item \textbf{MEGALAPHOBIA} \\ Get at least 200 feet from any building. Take a picture of said spot to verify. \textbf{200 coins}
    \item \textbf{I SEE U}
    \\ Photograph your partner from at least 500 feet away. They must be in the photo. \textbf{200 coins}
    \item \textbf{MCDONALD'S}
    \\ Take a photo of yourself outside a McDonald's \textbf{100 coins}
    \item \textbf{HI HIGH}
    \\ High five at a point at least 250 feet above sea level. \textbf{300 coins}
    \item \textbf{FRIENDS}
    \\ Find 3 different species of living, non-bug, non-bird, non-human animals. You must clearly capture them on camera. \textbf{300 coins}
    \item \textbf{FROM DOWNTOWN} \\ Score a three-pointer on a basketball hoop. You need not use a ball. If there is not a three-point line, you must make it from farther than the circle surrounding the free-throw. \textbf{200 coins}
    \item \textbf{BUDGET BASEBALL} \\ Throw any object at your partner. Your partner must hit that object with another object midair, simulating baseball. You must stand at least 20 ft apart. \textbf{200 coins}
    \item \textbf{BREAK COPYRIGHT LAW}\\ Find a place where copyrighted audio is playing for at least 20 seconds. Any audio volume that can be picked up by your phone's microphone counts. You may not initiate the playing of any sound on any device. \textbf{200 coins}
    \item \textbf{GO TO SOMETHING INTERESTING} \\ Without researching on YouTube, go to something that has a YouTube video about it with at least 100,000 views. The YouTube video's title must either include the thing's name, or clearly be referencing it as its main focus. If you cannot find a video correlating to your location you may either retry or veto the challenge. \textbf{100 coins}
    \item \textbf{SEE A GREAT WAVE} \\ View any wave and remark upon how great it is. It may be a real wave or a depiction, though the depiction may not come from anything traveling with you or a digital device. \textbf{200 coins}
    \item \textbf{STALK A BIRD} \\ You must have a single bird on camera continuously for five minutes. If you ever lose sight of the bird or have to cut, you have to start over. The bird must be alive, and may not be caged. \textbf{500 coins}
    \item \textbf{CUT A FRUIT IN HALF USING ONLY YOUR HANDS} \\ Acquire an fruit. Using only your hands, fully cut the fruit in half. \textbf{150 coins}
    \item \textbf{FIND AN AMERICAN FLAG} \\
    Find a real American flag, or a depiction of an American flag, in the wild. The flag cannot be created by you in any way. \textbf{100 coins}
    \item \textbf{SEE SOMETHING OLD} \\ You have 5 minutes after drawing this card to find the oldest thing you can. You may declare the challenge complete earlier than 5 minutes if you choose. You may not use technology until after you have decided on the item. \textbf{\# of years = \# of coins}
    \item \textbf{COMMUNICATE BY MORSE} \\ Stand at least 20 feet away from your partner. Using a random word generator, generate a random 8 letter word. Communicate the word to your partner using morse code. If you fail, you may re-attempt with a new word. You may have a translator on you. \textbf{200 coins}
    \item \textbf{SPELL ANY PLAYER'S NAME IN GRAFFITI} \\ Find all of the letters in any player's first name in already-written graffiti. For example, for Adam, find A, D, and M \textbf{150 coins}
    \item \textbf{LAST SECOND SWITCH} \\
    Go to an undergraduate college campus (not UCSF) and record one team member saying they are changing where they are attending to the college they are currently on \textbf{750 coins}
    \item \textbf{WATCH A SPORTS EVENT} \\You must find a TV playing something that is arguably a sports game. You may not use your phone to watch the game. \textbf{150 coins}
    \item \textbf{ACQUIRE ARC TESTIMONIAL} \\  Record a stranger using and reviewing Arc. \textbf{300 coins}
    \item \textbf{NONCOLONIAL POETRY} \\ Memorize the first 4 lines of a poem in a different language and recite them on camera. \textbf{200 coins}
    \item \textbf{FOUNTAIN TRANSPORTATION} \\Get some water from on any fountain (water fountain included) and put it in a different fountain. \textbf{300 coins}
    \item \textbf{FROLICK} \\ You must remark about how good of a time you are having for 5 min. \textbf{200 coins}
    \item \textbf{MIMICRY}\\ Find any statue and take a picture of you imitating it. \textbf{100 coins}
    \item \textbf{MATH} \\ One team member must generate a random number between 1 and 100. You have 10 seconds to find the square of that number. If you fail, veto the card with no time penalty. \textbf{250 coins}
    \item \textbf{RUN}\\ You have 5 minutes to run 0.5 miles: 0.25 miles in one direction and then 0.25 back to where you started. If you fail, you have to pay for the distance you ran. \textbf{200 coins}
    \item \textbf{METRO} \\ Sing/ad lib BBL Drizzy on the train, and take a video. You only have to recognizeably mouth the words. \textbf{150 coins}
    \item \textbf{CAPITALISM} \\ Find 2 bench ads. \textbf{100 coins}
    \item \textbf{COMMUNISM} \\ Find communist imagery: communist country flags, hammer/sickle, famous communist/marxist leaders (Mao, Marx, Stalin, etc.) \textbf{200 coins}
    \item \textbf{ACTUAL WALLET PAIN} \\ Buy something overpriced. It must be more expensive than what the exact same item costs on Amazon. You must be able to find the exact same item on Amazon. \textbf{300 coins}
    \item \textbf{THIS CONVERSATION IS GIVING OHIO} \\ In a conversation with a stranger use three words (separated by spaces if transcribed) from this list of brainrot terms: skibidi, Ohio, rizz/rizzler, mewing, mogging, ops, gyatt. \textbf{150 coins}
    \item \textbf{TO BE VERB HUNT} \\  Find and take pictures of 10 to be verbs. You must edit each image so that all to-be circled, and each image must also include one check minus. If any to-be verbs are uncircled and another team finds out, you lose 500 coins. You may circle multiple to-be verbs per picture. You may not take pictures of to-be verbs you wrote. \textbf{250 coins}

\end{enumerate}

\section{curses}
%all of the curse costs are preliminary suggestions
\begin{itemize}
    \setcounter{enumi}{-1}
    \item \textbf{NO PHONE :(} \\ You can only use discord and timer app on phone for 12 minutes. NO searching or maps!!!! Harvesters are also not allowed to track Crops when both Harvesting teams are cursed by NO PHONE. If one Harvesting team is cursed, only the other team may track the Crop with their phones. \textbf{400 coins }
    \item \textbf{COMPULSORY BUS TOUR} \\Get on the nearest bus that comes to the nearest stop to you (you cannot check where it goes). (applies to all Harvesters) \textbf{600 coins}
    \item \textbf{GIVING ELEMENTARY SCHOOL} \\ For 10 minutes, you cannot step on crack in sidewalk. If you fail, you must stand still for 10 minutes. (applies to all Harvesters) \textbf{100 coins}
    \item \textbf{TRAGIC LOSS OF IMPORTANT SYMBOL} \\ For 30 minutes you can't use the letter e. Anytime you do, you must stand still for 10 minutes. (applies to all Harvesters) \textbf{200 coins}
    \item \textbf{NO PUBIC TRANSPORT} \\ For 15 min, you cannot take any form of public transportation. (applies to all Harvesters) \textbf{300 coins}
    \item \textbf{SING DLD THEME} \\ Both of you must record yourself humming/singing/vocalizing or whatever the Don't Look Down theme for 5 minutes. (applies to all Harvesters) \textbf{300 coins}
    \item \textbf{CURSE OF ORIN THE SWIM COACH} \\ You can't talk to your teammate until you complete your next challenge (no texting either), starting two minutes from now. If you fail, you must stand in silence for 5 minutes and you can continuously fail. (applies to all Harvesters) \textbf{300 coins}
    \item \textbf{DR. T IS WATCHING} \\ For the next 30 minutes, if anyone on your team uses the word "this" or "that" (or any contraction/compound word including these evil words), your team immediately loses half of their coins. \textbf{300 coins}
    \item \textbf{ALEA IACTA SUNT} \\ While doing your next challenge, roll a dice (or use random number between 1 and 6). Multiply the number you get by 0.1 miles, and that is the radius you must stay in for the next 10 min. (applies to all Harvesters) \textbf{300 coins}
    \item \textbf{ON THE LOOKOUT} \\ For the next 15 min, if the Crop takes a full body photo of any Harvester from less than 300 ft away, the photographed Harvester cannot move for the next 10 min. (Obviously use your judgment here if you're in the middle of a crosswalk don't stop there) \textbf{300 coins}
\end{itemize}

\end{document}
