\documentclass{article}
\usepackage{graphicx} % Required for inserting images
\usepackage{hyperref}
\title{san francisco plane latency}
\author{}
\date{}
\begin{document}

\maketitle

\section{rules}
\begin{itemize}
    \item 25 coins per 0.1 miles on bart
    \item 30 coins per 0.1 miles on muni metro
    \item 35 coins per 0.1 miles on bus
    \item 40 coins per 0.1 miles on foot
    \item \textbf{For every challenge you must take a photo/video as proof that you completed the challenge. Afterwards, send the photo and challenge name to your opponents in the relevant Discord channel.}
    \item \textbf{If you would like another challenge option, you can veto a challenge, whereby you must stay in the same place for 15 minutes and you cannot complete any challenges.}
    \item \textbf{At any point you are allowed to walk away from your current station/bus stop as long as you walk back to it for no cost. This will be very useful for most challenges.}
    \item \textbf{You start the game by randomly picking three location-independent challenges. When you complete a challenge, randomize for a new challenge, using \url{https://plane-latency.vercel.app/challenges}.}
\end{itemize}

\section{mandatory challenges}
These challenges must be completed at some point in order for you to win. They can be completed at any time and in any order.
\begin{itemize}
    \item \textbf{FIND PERCY JACKSON BOOK} \\
        Find any book with "Percy Jackson" in the title at a public library. You don't need to actually check it out, but you must take a photo of it. Once a book is claimed by any team, it can not be claimed by any other.
    \item \textbf{VISIT AN INDEPENDENT SCHOOL}
        Take a picture outside an independent (private, non-religious) high school. Once a school is claimed by any team, it can not be claimed by any other (including any satellite locations).
\end{itemize}

\section{checkpoints}
These must be completed in order.

\begin{enumerate}
    \setcounter{enumi}{-1}

    \item \textbf{CITY HALL} \\
        Find one of twenty randomly generated years inside city hall. Once a numerical year is claimed by any team, you can no longer claim that numerical year (the years will be sent in the checkpoints channel in Discord). So if you found 1989 on the floor but Joffery found 1989 on the ceiling before you, you can't claim it. First team to post a picture with a given year clearly visible in it claims that year. First team gets \textbf{200 coins}, next team gets \textbf{150 coins}, third place gets \textbf{100 coins}, last place gets \textbf{50 coins}. If you cannot complete the challenge in 20 minutes, you can leave but you receive no coins.

    \item \textbf{DOLORES PARK} \\
        Climb up a slide. You must start at the lowest part of the slide, and climb to the top. If there are children present preventing you from climbing, your team must slide down 5 times in total. As a reward you \textbf{claim which of the next four locations you will go to}.

    \item \textbf{TWIN PEAKS OR GLEN CANYON OR MOUNT SUTRO OR BILLY GOAT HILL} \\ 
    \begin{itemize}
        \item At TWIN PEAKS, climb the secret stairs, touch a rock at the top of Noe Peak, touch a rock at the top of Eureka Peak, and touch the fence around the Twin Peaks Reservoir
        \item At GLEN CANYON PARK, stand on a picnic table within 100 feet of Glenridge Nursery School.
        \item At MOUNT SUTRO, visit Sutro Tower and take a photo. Also, you must step foot on 7 different trails and take a screenshot on maps/photo to prove. Finally, take a photo of 5 different plants that are endemic to SF. Send a screenshot of a Google search with a photo to confirm.
        \item At BILLY GOAT HILL, head to the dog park and photograph a dog OR head to the human park and swing 5 times. 
    \end{itemize}

    \item \textbf{CALIFORNIA ACADEMY OF SCIENCES} \\
    Take a picture outside the California Academy of Sciences. Both teammates and the words "California Academy of Sciences" must be visible in the photo.

    \item \textbf{ROMAN'S DENTIST} \\
    Take a picture with the words "Tooth Fairy" in it. \textit{Hint: If you are uneducated, Roman's dentist is located at 2001 Union St \#450, San Francisco, CA 94123.}
    
    % \item \textbf{Daly City} \\
    % Find 3 license plates from out of state. No repeats compared to your opponents. Whoever takes a picture of the license plate and sends it in the group chat first gets to claim that license plate. The first team to complete is guaranteed to get on an earlier train than their opponents. \textbf{A ride to Balboa Park} 
    % \item \textbf{Dolores Park} \\ Walk across the rainbow bridge in Dolores Park. Whoever gets to Dolores Park first will get to choose which UCSF campus they want to go to. 
    % \item \textbf{UCSF} \\ You must take a photo of the Helen Diller Building. The name Helen Diller must be clearly visible. You can do this at either Parnassus or Mission Bay
    % \item \textbf{Salesforce Park} \\ You must be a complete lap around Salesforce Park. That means you must go up to the park.
    % \item \textbf{Presidio} \\
    % You must visit three places in the Presidio with the word overlook in their title. At the first overlook you go to, you may ban an overlook for your opponents to go to by sending a text message with the banned overlook. That means they cannot claim that overlook as one of their three
    % \item \textbf{Crissy Beach} \\
    % Finish at Crissy Beach to win
\end{enumerate}

\section{location-independent challenges}
\begin{enumerate}
    \setcounter{enumi}{-1}
    \item \textbf{SPICIEST FOOD} \\ Go to a restaurant and ask for the spiciest thing on the menu. You must take a photo of the item and send it to your opponents. You must finish the entire food before proceeding. It must be described by the restaurant as spicy/hot  \textbf{300 coins}
    \item \textbf{BREAK ANY LAW} \\ Break a law. The law can be from any level of jurisdiction and does not have to be a law in California. \textbf{100 coins}
    \item \textbf{TAKE A PICTURE OF AN OFFICIAL SAN FRANCISCO LANDMARK} \\ You must be within 100 feet of the landmark when the photo is taken. Find landmarks at \url{https://en.wikipedia.org/wiki/List_of_San_Francisco_Designated_Landmarks} \textbf{200 coins}
    \item \textbf{FIND ANY COIN ON THE GROUND} \\ The coin does not have to be American. It must be a metal coin and valid currency in somewhere (not necessarily a country currency) \textbf{150 coins}
    \item \textbf{HOUSESHOPPING}\\ Estimate the value of a house at your current location. You must then check on Zillow for the value of the house. Your guess must be within 25\%. If incorrect, you must veto. \textbf{500 coins}
    \item \textbf{DO 50 JUMPING JACKS} \\ Do 50 jumping jacks. You must record the whole thing. Only one person may perform the jumping jacks at a time but gyou can cumulative add the team member's jumping jacks to get to 50. \textbf{100 coins}
    \item \textbf{FIND A FANCY CAR} \\ Take a picture of car that has a price of \$100,000 or more \textbf{300 coins}
    \item \textbf{TOUCH STRANGER'S DOG} \\ Touch a stranger's dog. You must get permission. \textbf{150 coins}
    \item \textbf{CRITICS} \\ Record a 5-minute video criticizing the nearest building to you. You must continuously criticize the building for 5 minutes straight. You may switch who is speaking, but it must be one uncut video of at least 5 minutes long. \textbf{200 coins}
    \item \textbf{ADVERTISE ARC} \\ You must make a sign with the arc logo and adhere it to some spot at least 3 feet above the ground. It must stick without any human body part touching it. The arc logo can be makeshift but it must still be recognizably arc. \textbf{300 coins}
    \item \textbf{COO-L PIGEON} \\ Get close enough to a pigeon to take a picture with both the pigeon and your feet in it. You must have both feet of one person in said photo. \textbf{300 coins}
    \item \textbf{PROUD ARC USER} \\ Randomly pick 30 seconds of audio from a video on the browser company's youtube channel. Memorize it and repeat it on camera. First, sort the videos of newest to oldest and randomize a number to pick which video. Then randomize a number to pick when to start your video. If at any point you do not have at least 30 seconds, rerandomize. \textbf{500 coins}
    \item \textbf{NEAREST MUNI \& BART} \\ Take picture of the nearest BART \& MUNI station. There must be a BART sign with the station name in one picture and a MUNI sign with the station name in another. You must also send the address of the point you started from so one can verify the nearest MUNI \& BART station. \textbf{300 coins}
    \item \textbf{RUN A HALF-MILE} \\ You must return to where you started at the end of the half-mile. \textbf{200 coins}
    %\item \textbf{TOUCH THE OCEAN} \\ Touch the ocean. You can do it on either the west, north, or east of San Francisco. If you cannot touch the ocean, you can also collect the coins if you are directly above the water, etc on a pier) \textbf{500 coins}
    \item \textbf{FIND A FOREIGN FLAG} \\ Find a foreign flag. You must be able to identify what country flag it is. \textbf{100 coins}
    \item \textbf{GREEN IN GREEN} \\ Go to a place colored green on google maps and take a picture with something green in that park. \textbf{100 coins}
    \item \textbf{GIVE ME A SIGN} \\ Photograph a street sign with a street name that contains a number (word or digits) \textbf{100 coins}
    \item \textbf{CLIMB A TREE} \\ Climb a tree. You must record yourself touching only the tree and not the ground or roots of the tree for 5 seconds. \textbf{100 coins}
    \item \textbf{VISIT A MUSEUM} \\ Go into a museum and stay there for at least 5 minutes. Share a fact that you learned on camera. \textbf{300 coins}
    \item \textbf{USE A FANCY RESTROOM} \\ Go into a bathroom of a hotel that offers a room over \$500 \textbf{500 coins}
    \item \textbf{GO EXACTLY HALF A MILE} \\ First, set a starting point. Then from there, spin around and point in a random direction. You must then go to a point at least a half-mile in that direction. Unlike other challenges, you don't have to return to where you started. \textbf{200 coins}
    \item \textbf{MEGALAPHOBIA} \\ Get at least 200 feet from any building. Take a picture of said spot to verify. \textbf{200 coins}
    \item \textbf{GET ON A TRAIN IMMEDIATELY} \\ You have 5 minutes AFTER DRAWING THIS CARD to get on a BART or MUNI train. Start a timer now. You must take it at least one stop. You must also be able to afford it. After 5 minutes have passed, discard this card with no veto penalty. \textbf{400 coins}
    \item \textbf{I SEE U}
    \\ Photograph your partner from at least 500 feet away. They must be in the photo. \textbf{200 coins}
    \item \textbf{MCDONALD'S}
    \\ Take a photo of yourself outside a McDonald's \textbf{100 coins}
    \item \textbf{HI HIGH}
    \\ High five at a point at least 250 feet above sea level. \textbf{300 coins}
    \item \textbf{FRIENDS}
    \\ Find 3 different species of living, non-bug, non-bird, non-human animals. You must clearly capture them on camera. \textbf{300 coins}
    \item \textbf{FROM DOWNTOWN} \\ Score a three-pointer on a basketball hoop. You need not use a ball. If there is not a three-point line, you must make it from farther than the circle surrounding the free-throw. \textbf{200 coins}
    \item \textbf{BUDGET BASEBALL} \\ Throw any object at your partner. Your partner must hit that object with another object midair, simulating baseball. You must stand at least 20 ft apart. \textbf{200 coins}
    \item \textbf{BREAK COPYRIGHT LAW}\\ Find at least 2 places where we'll have to mute the audio for copyright reasons. Each place must be at least 100 feet apart from any other selected place. Public transport announcements don't count. Any audio volume that can be picked up on camera counts. You may not initiate the playing of any sound on any device. \textbf{200 coins}
    \item \textbf{GO TO SOMETHING INTERESTING} \\ Without researching on YouTube, go to something that has a YouTube video about it with at least 100,000 views. The YouTube video's title must either include the thing's name, or clearly be referencing it as its main focus. If you cannot find a video correlating to your location you may either retry or veto the challenge. \textbf{100 coins}
    \item \textbf{SEE A GREAT WAVE} \\ View any wave and remark upon how great it is. It may be a real wave or a depiction, though the depiction may not come from anything traveling with you or a digital device. \textbf{200 coins}
    \item \textbf{STALK A BIRD} \\ You must have a single bird on camera continuously for five minutes. If you ever lose sight of the bird or have to cut, you have to start over. The bird must be alive, and may not be caged. \textbf{500 coins}
    \item \textbf{CUT A FRUIT IN HALF USING ONLY YOUR HANDS} \\ Acquire an fruit. Using only your hands, fully cut the fruit in half. \textbf{150 coins}
    \item \textbf{FIND AN AMERICAN FLAG} \\
    Find a real American flag, or a depiction of an American flag, in the wild. The flag cannot be created by you in any way. \textbf{100 coins}
    \item \textbf{SEE SOMETHING OLD} \\ You have 5 minutes after drawing this card to find the oldest thing you can. You may declare the challenge complete earlier than 5 minutes if you choose. You may not use technology until after you have decided on the item. \textbf{\# of years = \# of coins}
    \item \textbf{COMMUNICATE BY MORSE} \\ Stand at least 20 feet away from your partner. Using a random word generator, generate a random 8 letter word. Communicate the word to your partner using morse code. If you fail, you may re-attempt with a new word. You may have a translator on you. \textbf{200 coins}
    \item \textbf{CRY} \\ Produce any actual tears, using any means necessary. \textbf{100 coins}
    \item \textbf{SPELL ANY PLAYER'S NAME IN GRAFFITI} \\ Find all of the letters in any player's first name in already-written graffiti. For example, for Adam, find A, D, and M \textbf{150 coins}
    \item \textbf{LAST SECOND SWITCH} \\
    Go to an undergraduate college campus (not UCSF) and record one team member saying they are changing where they are attending to the college they are currently on \textbf{750 coins}
    \item \textbf{WATCH A SPORTS EVENT} \\You must find a TV playing a live sports game. You may not use your phone to watch the game. \textbf{150 coins}
    \item \textbf{LIE} \\ Complete any other card but your proof must be invalid in some way. It may not be arguably valid. If the other teams sus you out, you get no coins. If no one susses you out after 10 minutes, you get double the coins of the other card. \textbf{Double the coins of the other card}
    \item \textbf{ACQUIRE ARC TESTIMONIAL} \\  Record a stranger using and reviewing Arc. \textbf{300 coins}
    \item \textbf{NONCOLONIAL POETRY} \\ Memorize the first 4 lines of a poem in a different language and recite them on camera. \textbf{200 coins}
    \item \textbf{FOUNTAIN TRANSPORTATION} \\Get some water from on any fountain (water fountain included) and put it in a different fountain. \textbf{300 coins}
    \item \textbf{FROLICK} \\ You must remark about how good of a time you are having for 5 min. \textbf{200 coins}
    \item \textbf{MIMICRY}\\ Find any statue and take a picture of you imitating it. \textbf{100 coins}
    \item \textbf{MATH} \\ One team member must generate a random number between 1 and 100. You have 10 seconds to find the square of that number. If you fail, veto the card with no time penalty. \textbf{250 coins}
    \item \textbf{RUN}\\ You have 5 minutes to run 0.5 miles: 0.25 miles in one direction and then 0.25 back to where you started. If you fail, you have to pay for the distance you ran. \textbf{200 coins}
    \item \textbf{ART}\\ From this list of animals, generate a random number and try to draw it. Your partner will try to guess. If correct, get the coins, if incorrect, stay put for 5 min. 1) Lion 2) Dog 3) Horse 4) Giraffe 5) Narwhal 6) Dolphin 7) Elephant 8) Eagle 9) Frog 10) Bear \textbf{100 coins}
    \item \textbf{METRO} \\ Sing/ad lib BBL Drizzy on the train, and take a video. You only have to recognizeably mouth the words. \textbf{150 coins}
    \item \textbf{CAPITALISM} \\ Find 2 bench ads. \textbf{100 coins}
    \item \textbf{ACTUAL WALLET PAIN} \\ Buy something overpriced. It must be more expensive than what the exact same item costs on Amazon. You must be able to find the exact same item on Amazon. \textbf{300 coins}
    
\end{enumerate}

\section{curses}
%all of the curse costs are preliminary suggestions
\begin{itemize}
    \setcounter{enumi}{-1}
    \item \textbf{NO PHONE :(} \\ You cannot use phone for 20 minutes. (applies just to target team) \textbf{400 coins }
    \item \textbf{COMPULSORY BUS TOUR} \\Get on the nearest bus that comes to the nearest stop to you (you cannot check where it goes). (applies just to target team) \textbf{300 coins}
    \item \textbf{GIVING ELEMENTARY SCHOOL} \\ For 10 minutes, you cannot step on crack in sidewalk. If you fail, you must stand still for 10 minutes. (applies just to target team) \textbf{100 coins} 
    \item \textbf{TRAGIC LOSS OF IMPORTANT SYMBOL} \\ For 30 minutes you can't use the letter e. Anytime you do, you must stand still for 10 minutes. (applies just to target team) \textbf{200 coins}
    \item \textbf{NO PUBIC TRANSPORT} \\ For 15 min, you cannot take any form of public transportation. (applies just to target team) \textbf{300 coins}
    \item \textbf{SING DLD THEME} \\ Both of you must record yourself humming/singing/vocalizing or whatever the Don't Look Down theme for 5 minutes. (applies just to target team) \textbf{300 coins}
    \item \textbf{CURSE OF ORIN THE SWIM COACH} \\ You can't talk to your teammate until you complete your next challenge (no texting either), starting two minutes from now. If you fail, you must stand in silence for 5 minutes and you can continuously fail. (applies just to target team) \textbf{300 coins}
    \item \textbf{ALEA IACTA SUNT} \\ While doing your next challenge, roll a dice (or use random number between 1 and 6). Multiply the number you get by 0.1 miles, and that is the radius you must stay in for the next 10 min. (applies just to target team) \textbf{300 coins}
    \item \textbf{ON THE LOOKOUT} \\ For the next 15 min, if the team who activated the curse takes a full body photo of you from less than 300 ft away, you cannot move for the next 10 min. (Obviously use your judgement here if you're in the middle of a crosswalk don't stop there) (applies to all teams except the team which purchased the curse) \textbf{300 coins}
\end{itemize}

\end{document}
